Title here

### 2017-01-03 portfolio/text/ms.Rmd
Fix bib; add outline

@@

We fit our models with Stan 2.11.1 [@hoffman2014; @standevelopmentteam2015;
@standevelopmentteam2015a; @carpenter2015] and R 3.3.1 [@rcoreteam2016]. Stan
implements the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm
[@hoffman2014] to perform Bayesian statistical inference. We assigned weakly
informative priors on all parameters: $N(0, 2^2)$ priors on all $\beta$,
$\gamma$, and $\eta$ parameters, and half-$t(3, 0, 2)$ priors (i.e. degrees of
freedom of 3 and scale of 2) on all $\sigma$ and $\tau$. We ran four chains and
2,000 iterations and discarded the first 1,000 iterations of each chain as warm
up. We checked for chain convergence visually with trace plots, ensured that
$\hat{R}<1.05$ (the potential scale reduction factor) and that the effective
sample size, as calculated by the rstan R package [@standevelopmentteam2015],
was greater than 200 for all parameters [@gelman2014]. We verified that our
model returned sensible estimates by comparing our estimates to an ad-hoc
two-stage model fit with the lme4 R package [@bates2015], where we first fit
a mixed-effects regression model to the mean, and then modelled the absolute
residuals from that first model in a second mixed-effects model representing the
variance component. We also validated the model with simulated data, and were
able to recover the true values (Supporting Information). Code used in our
analysis is available at <https://github.com/NCEAS/pfx-commercial/portfolios/>.

>>>>

increased revenue with specialization? 
why might someone specialize? but this has long-term risks 
	efficiency 
		and individual behavior important in fleet dynamics and efficiency of catch @hilborn1985
		"Specialization, as measured by the share of total cultivated land devoted to rice production, also tends to lower inefficiency," @abdulai2000
	cash crops 
		sockeye e.g.
		cocoa: most profitable crop export in Nigeria @mustapha1999
			when cocoa prices were high, most cocoa farmers were highly specialized; now there is much more diversification to other sources of income... for example trading and electronic repairs @mustapha1999
		tobacco: high profitability and low variability of income from tobacco mean that the optimal farming strategy (regardless of risk profile) is to specialize as much as possible on tobacco (given alternatives such as soybean, alfalfa, chickpeas, ...) -- great reference to use -- quadratic optimization @chavez2014
	conversely, diversification can happen as a consequence of non-ideal situations 
		poor fishing years mean the fishermen must seek out other options - this paper 
		downwards economic shocks tend to be associated with increasing diversity for households relying on forests for income @debela2012
		for example, many small farms use diversification to maximize revenue given their limited land @barbieri2008
	but has long-term risks 
		"...most graphic, recent example of such risks was the reliance of U.S. crop producers on export markets for wheat, corn, and soybeans during the 1970s. Many farmers borrowed large sums of money to buy additional land and buy specialized equipment ....

		Specialized farmers producing export commodities were hardest hit by the financial crisis of American agriculture in the early 1980s...." @ikerd1990
		"Historically, cocoa farmers rarely engaged in non-farm commercial or artisanal activities. When cocoa farmers took to non-farm occupations in the 1970s and 19803, it was as a result of the severe crisis of accumulation confronting them (Berry 1985). Indeed, only 5 per cent of the 1964 Alade sample had any non-farm occupation (Oloko 1964: 57). My 1992 study established that by the early 1980s, that is just before SAP, about 35 per cent of the Lower stratum in that survey, 30 per cent of the Middle, and 33 percent of the Upper had non‐farm occupations." @mustapha1999

barriers to diversification 
	cost of entry
		"poorer households have fewer opportunities in non-cropping activities ... and hence less diversified incomes. ... reflect[s] their relative lack of capital, which makes it difficult for them to diversify away from subsistence agriculture...  " @abdulai2001
		entry barriers mean that poor farmers tend to be less diversified and are forced to experience lower returns and higher variability in earnings @barrett2001
			e.g. "Block and Webb and More income diversification associated with higher welfare measured in both income and nutritional terms in Ethiopia, and that the least diversified ft hard to increase their diversification over time. ... Barrett et al. report a strong association between greater income diversification ˆ and higher wealth and income in Cote d’Ivoire and Kenya." @barrett2001
		access to financial capital important to income diversification for fishing communities in Kenya @olale2012
		overall, diversification was positively related with total income for those living in "forest margins" @illukpitiya2008
	ifqs
		catch shares may help prevent fisheries collapse @costello2008
		entry expensive
		diversification declined at a time following catch share programs on the West Coast @holland2016
		vessels that entered West Coast fisheries less diversified than those that entered before IFQs (and of course cost is increased to get into these fisheries for those that were not already participants) @holland2016
		catch share programs may reduce variability and offset the effects of lower diversity -- found that year-to-year vessel revenue decreased after catch shares (and average revenue increased for most) @holland2016

@@

We fit our models with Stan 2.14.1 [@standevelopmentteam2016;
@standevelopmentteam2016a] and R 3.3.1 [@rcoreteam2016]. Stan
implements the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm
[@hoffman2014] to perform Bayesian statistical inference. We assigned weakly
informative priors on all parameters: $N(0, 2^2)$ priors on all $\beta$,
$\gamma$, and $\eta$ parameters, and half-$t(3, 0, 2)$ priors (i.e. degrees of
freedom of 3 and scale of 2) on all $\sigma$ and $\tau$. We ran four chains and
2,000 iterations and discarded the first 1,000 iterations of each chain as warm
up. We checked for chain convergence visually with trace plots, ensured that
$\hat{R}<1.05$ (the potential scale reduction factor) and that the effective
sample size, as calculated by the rstan R package [@standevelopmentteam2016],
was greater than 200 for all parameters [@gelman2014]. We verified that our
model returned sensible estimates by comparing our estimates to an ad-hoc
two-stage model fit with the lme4 R package [@bates2015], where we first fit
a mixed-effects regression model to the mean, and then modelled the absolute
residuals from that first model in a second mixed-effects model representing the
variance component. We also validated the model with simulated data, and were
able to recover the true values (Supporting Information). Code used in our
analysis is available at <https://github.com/NCEAS/pfx-commercial/portfolios/>.
